Matroids from families of null hypotheses

### 2013-08-14 presentation/presentation.tex
added a slide to illustrate set partitions and bell numbers

  \begin{itemize}
  \item Two-sided comparisons between $m$ means
  \item The cycle matroid of the corresponding graph representation
    provides an equivalent dependence structure
  \item The flats of a (simple) complete graph are
    isomporphic to the partitions of a set of size $m$
  \item Provides an efficient way to generate all exhaustive sets by
    enumeration of all partitions [ER '88] or hyperplanes 
  \item The number of exhaustive sets are given by the Bell numbers

  \end{itemize}

>>>>

\begin{tabular}{ll}
  \begin{minipage}{.3\textwidth}
    \includegraphics[width=1.1\textwidth]{setpartitions.pdf} \\
     {\tiny wikipedia:Bell\_number}
  \end{minipage} &
  \begin{minipage}{.7\textwidth}
  \begin{itemize}
  \item Two-sided comparisons between $m$ means
  \item The cycle matroid of the corresponding graph representation
    provides an equivalent dependence structure
  \item The flats of a (simple) complete graph are
    isomporphic to the partitions of a set of size $m$
  \item Provides an efficient way to generate all exhaustive sets by
    enumeration of all partitions or hyperplanes \cite{er1988fast,knuth2005art,kokosinski2006new} 
  \item The number of flats is given by the Bell-numbers \ie 5, 15,
    52, 203, 877, 4140, ... 
  \end{itemize}
  \end{minipage}
\end{tabular}
